---
title: "R package"
author: "Camron Bartlow"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

My package is called **MATH4753BART0039** and I have packaged and documented
functions `myboot2`, `myci`, `mycltp`, `mymaxlik`, `myncurve`, `mysample`, and
`quadPlot`.

Your actual package name and functions will obviously be called something else.

# First function
```{r}
x <- rnorm(20, 10, 10)
x
MATH4753BART0039::myboot2(x = x)
```

The function returns a histogram of bootstrap sample statistics based on a given
dataset *x*, that shows the range of the confidence intervals, and showing the
mean estimate.

# Second function
```{r}
x <- rnorm(20, 10, 10)
x
MATH4753BART0039::myci(x)
```

The function returns a 95% confidence interval for a given distribution *x*.

# Third function
```{r}
MATH4753BART0039::mycltp(n=2,iter=10000, lambda=4)
```

The function returns a histogram of the sample mean, a barplot of a sampled y,
and a probability function for poisson distribution given a sample size *n*,
number of iterations *iter*, and the lambda of the Poisson distribution *lambda*.

# Forth function
```{r}
logbin=function(x,param) log(dbinom(x,prob=param,size=20))
logpoiss=function(x,param) log(dpois(x,lambda=param)) 
logexp=function(x,param) log(dexp(x,rate=param))
max = MATH4753BART0039::mymaxlik(x=c(3,3,4,3,4,5,5,4),param=seq(0,1,length=1000),lfun=logbin,main="Binomial",cex.main=1)
```

The function returns a logarithmic graph based on a given set distribution *x*, sequence of steps *param*, given logarithmic function *lfun*, and any other graphical parameters *...*, with a line marking the maximum likelihood.

# Fifth function
```{r}
MATH4753BART0039::myncurve(mu=10,sigma=5,a=6)
```

The function displays the curve , shaded area between the curve and x axis from $-\infty$ to $x=a$ and calculates the area(probability) in a list.

# Sixth function
```{r}
MATH4753BART0039::mysample(n=1000, iter=3, time=1)
```

The function generates an *iter* number of barplots of *n* sample size, with a *time* second delay between each barplot

# Seventh function
```{r}
fireData <- MATH4753BART0039::fire
quad.lm <- lm(fireData$DAMAGE~fireData$DISTANCE + I(fireData$DISTANCE^2), data=fireData)
MATH4753BART0039::quadPlot(x=15, qlm=quad.lm)
```

The function returns estimate of y at x of a given linear model lm.

# The github repository

This is the address of my GITHUB repository:
<https://github.com/MtnDont/MATH4753BART0039.git>

